Manuscript_draft

### 2021-05-06 manuscript_draft.Rmd
updtae negExp

@@

@@

Among treatments and throughout the stand development after treatment,
the stands maintained a negative exponential (also referred to as
'reverse-J') diameter class distribution
(`r figNums("diamK.plot",display="cite")`).\
Immediately after the partial harvest, the diameter class distribution
of volume differed among treatments. In the 27 years since partial
harvest, volume in all three treatment units was mostly concentrated in
the 22.5-27.5cm DBH class, and mostly comprised of fir
(`r figNums("diamVol.plot",display="cite")`). Over both time periods
shown in the figure and all three treatments, most of the spruce volume
was concentrated in DBH classes spanning 37.5 to 47.5cm. Basal area
trends were very similar to volume (not shown).

>>>>

1. COmplete Q factor coding

@@

#### Growth dominance coefficients
*Need to describe GDC methods here*

#### Diameter distributions
We quantified the stand structure in each plot and time period by computing Q factor, which is the ratio between adjacent diameter classes.  Diameter classes were 5cm wide.

@@

Among treatments and throughout the stand development after treatment,
the stands maintained a negative exponential (also referred to as
'reverse-J') diameter class distribution
(`r figNums("diamK.plot",display="cite")`).
Immediately after the partial harvest, the diameter class distribution
of volume differed among treatments. In the 27 years since partial
harvest, volume in all three treatment units was mostly concentrated in
the 22.5-27.5cm DBH class, and mostly comprised of fir
(`r figNums("diamVol.plot",display="cite")`). Over both time periods
shown in the figure and all three treatments, most of the spruce volume
was concentrated in DBH classes spanning 37.5 to 47.5cm. Basal area
trends were very similar to volume (not shown).

Q factor
```{r compute Q factor}

# Fit negative exponential distribution to plots/time combinations, and then combine
source(here::here("manuscript","negExp.R"))

# compute for each plot and time period
x.qFact<-
  X %>% 
  mutate(DBH.class=as.numeric(as.character(DBH.class))) %>% 
  group_by(BA.Target,Plot,Year,DBH.class) %>% 
  summarise(k=n()) %>% 
  complete(BA.Target,Plot,Year,DBH.class,fill=list(k=0)) %>% 
  group_by(BA.Target,Year,DBH.class) %>% 
  summarise(k=mean(k)) %>% 
  mutate(k=k*20) %>% 
  filter(k>0)

# function to apply negExp to each year
nexExp.year<-function(year){

  x<-
    x.qFact %>% 
    filter(BA.Target=="TU:10") %>% 
    filter(Year==year)

    negExp(x$DBH.class,y=x$DBH.class)

  }

}
